Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-05 Report06-12.Rmd
Chunk cleaning

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)
library(gridExtra)
library(ggmosaic)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE)

@@

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +  ylab("Proportion of faces matched") + xlab(factorVar) + scale_colour_manual(values=type.colours)
}

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=TRUE, booktabs = TRUE, caption = "This table lists the possible face descriptions that were appropriate for each individual face. The most appropriate descrition for each face was built by selecting one option from each list describing a particular attribute of the face that was selected. Most of these categories selections were made obvious in the image, Obscured and Head Angle were more difficult to choose for some faces.")
```

@@

@@

times <- amin %>%  
  filter(type!="Manual") %>% 
  select(file, type, time.user.self, time.sys.self) %>% 
  group_by(file, type) %>% 
  mutate(n=dplyr::n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))

@@

```{r RegressionFunctions}
# Prepare data
library(purrr)
library(tidyverse)
library(gridExtra)
library(dplyr)
library(ggplot2)

hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type  
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

@@

drop1(mod1, test="Chisq")

# currently same model as earlier, give two?

```
When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.

@@

Each table above considers the individual faces found in the set.
The upper left quadrany of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
Table 4, the comparison of Skybiometry and Manually annotated faces gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.

@@

```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual. The top left image presents a potential faces that actually defines an area containing a player's back and a ball boy's torso. The top right shows two potential faces that are actually the KIA logo on the net. The bottom left image was very interesting as the player's face was found, but the shirts of both the player and ball boy were deemed potential faces. The bottom right image had a lot more faces that usually recognised. Animetrics found a fist to the right on the centre that it considered a potential face. \\label{fig:UnusualImages}" }
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure a.")
i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure b.")
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure c.")
i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure d.")

@@

```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}

aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close−up not player",
          "Court in play",
          "Off court close up of player",
          "Crowd",
          "Court player close−up"))

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)
library(gridExtra)
library(ggmosaic)
library(tidyverse)
library(purrr)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)

@@

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}

ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +  ylab("Proportion of faces matched") + xlab(factorVar) + scale_colour_manual(values=type.colours)
}

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "This table lists the possible face descriptions that were appropriate for each individual face. The most appropriate descrition for each face was built by selecting one option from each list describing a particular attribute of the face that was selected. Most of these categories selections were made obvious in the image, Obscured and Head Angle were more difficult to choose for some faces.")
```

@@

```{r timeData}
times <- amin %>% 
  filter(type!="Manual") %>% 
  select(file, type, time.user.self, time.sys.self) %>% 
  group_by(file, type) %>% 
  mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))  
```

@@

@@

```{r RegressionFunctions, cache=FALSE}
# Prepare data
hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type  
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

@@

#drop1(mod1, test="Chisq")
#summary(mod1)
# currently same model as earlier, give two?

When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.

@@

Each table above considers the individual faces found in the set.
The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
Table 4, the comparison of Skybiometry and Manually annotated faces gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.

@@

```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual. The top left image presents a potential faces that actually defines an area containing a player's back and a ball boy's torso. The top right shows two potential faces that are actually the KIA logo on the net. The bottom left image was very interesting as the player's face was found, but the shirts of both the player and ball boy were deemed potential faces. The bottom right image had a lot more faces that usually recognised. Animetrics found a fist to the right on the centre that it considered a potential face. \\label{fig:UnusualImages}" }
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")
i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image b.")
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image c.")
i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image d.")

@@

```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}
aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close−up not player",
          "Court in play",
          "Off court close up of player",
          "Crowd",
          "Court player close−up"))
